Concentration of Maxima and Fundamental Limits in High-Dimensional Testing and Inference

### 2021-02-03 2.background/2.Gaussian-distributions.tex
DONE!
Ready for one final pass. Specifically, in the PDF, pls look at pages:

29, 30, 60 (notation <...>) Proofs of Propositons 5.1 and 5.3, Def. 5.3.

Page 115.

There is only one UNDEFINED reference on page 115. I can fix it once I understand the context better.

\begin{theorem} [Sudakov-Fernique Inequality] \label{th:Sudakov-Fernique} 
Let $\epsilon = (\epsilon(i))_{i=1}^p$ and $\eta = (\eta(i))_{i=1}^p$ be 
two multivariate normally distributed random vectors.

>>>>

\begin{theorem} [The Sudakov-Fernique inequality] \label{th:Sudakov-Fernique} 
Let $\epsilon = (\epsilon(i))_{i=1}^p$ and $\eta = (\eta(i))_{i=1}^p$ be 
two multivariate normally distributed random vectors.

### 2021-02-03 2.background/2.asymptotics.tex
DONE!
Ready for one final pass. Specifically, in the PDF, pls look at pages:

29, 30, 60 (notation <...>) Proofs of Propositons 5.1 and 5.3, Def. 5.3.

Page 115.

There is only one UNDEFINED reference on page 115. I can fix it once I understand the context better.

\medskip
{\bf Signal detection.}
The asymptotic behavior of the statistical risk in signal detection problems \eqref{eq:risk-detection} in high dimensions was first studied by \stilian{Yurii Ismailovich Ingster}{where did you find the full name?} in the context of sparse additive models \eqref{eq:model-additive} with 
independent and Gaussian components. Specifically, \cite{ingster1998minimax} considered the behavior of the 
theoretically optimal likelihood ratio (\ac{LR}) test in the high-dimensional asymptotic regime, where the dimension $p$ grows to infinity. Then, under certain parameterization of the size and sparsity of the signal $\mu$, a dichotomy exists: 
either ${\rm risk}^D(\mathcal{R})$ vanishes as $p\to\infty$ where $\mathcal{R}$ is the \ac{LR} test, or $\liminf_{p\to\infty} {\rm risk}^D(\mathcal{R}) = 1$ for any procedure.
The precise signal size and sparsity parameterizations as well as the so-called {\em detection boundary} discovered by Ingster are described in Chapter \ref{chap:phase-transitions}.

>>>>

\medskip
{\bf Signal detection.}
The asymptotic behavior of the statistical risk in signal detection problems \eqref{eq:risk-detection} in high dimensions was first studied by 
Yuri Izmailovich Ingster in the context of sparse additive models \eqref{eq:model-additive} with 
independent and Gaussian components. Specifically, \cite{ingster1998minimax} considered the behavior of the 
theoretically optimal likelihood ratio (\ac{LR}) test in the high-dimensional asymptotic regime, where the dimension $p$ grows to infinity. Then, under certain parameterization of the size and sparsity of the signal $\mu$, a dichotomy exists: 
either ${\rm risk}^D(\mathcal{R})$ vanishes as $p\to\infty$ where $\mathcal{R}$ is the \ac{LR} test, or $\liminf_{p\to\infty} {\rm risk}^D(\mathcal{R}) = 1$ for any procedure.
The precise signal size and sparsity parameterizations as well as the so-called {\em detection boundary} discovered by Ingster are described in Chapter \ref{chap:phase-transitions}.

### 2021-02-03 2.background/2.statistical_procedures.tex
DONE!
Ready for one final pass. Specifically, in the PDF, pls look at pages:

29, 30, 60 (notation <...>) Proofs of Propositons 5.1 and 5.3, Def. 5.3.

Page 115.

There is only one UNDEFINED reference on page 115. I can fix it once I understand the context better.

While \eqref{eq:Lq-norm} measures the deviation of the data from the origin in an omnidirectional manner, statistics that are tailored to the alternatives can be used in the hopes of power improvement if the directions of the alternatives are known.
For example, in the additive error model \eqref{eq:model-additive}, suppose we want to test for positive mean shifts, i.e., one-sided alternative
\begin{equation} \label{eq:global-test-one-sided}
    %\mathcal{H}_0: \mu(i) = 0, \;i=1,\ldots,p,
    %\quad\text{v.s.}\quad 
    \mathcal{H}_1: \mu(i)> 0, \; \text{for some }i\in\{1,\ldots,p\}.
\end{equation}
Then, one might consider monitoring the sum (or equivalently, the arithmetic average) of the observations, 
\begin{equation} \label{eq:sum-statistic}
    S(x) := \sum_{i=1}^p{x(i)},
\end{equation}
or the maximum of the observations,
\begin{equation} \label{eq:max-statistic}
    M(x) := \max_{i=1,\ldots,p}{x(i)}.
\end{equation}
Other tests based on the empirical \ac{CDF} are also available.
Assuming the same one-sided alternative, let 
\begin{equation}
    q(i) = 1 - \sup\{F_i(y)\,:\,y<x(i)\}, \quad i = 1,\ldots,p,
\end{equation}
be the p-values of the individual observations, where $F_i$ is the \ac{CDF} of the $i$-th component $x(i)$ under $\mathcal{H}_0$.
We define empirical \ac{CDF} of the p-values as
\begin{equation}
    \widehat{F}_p(t) = 
    \frac{1}{p} \sum_{i=1}^p \mathbbm{1}_{[0, t]}(q(i)).
\end{equation}
Viewed as random elements in the space of c\`adl\`ag functions with the Skorohod $J_1$ topology, the centered and scaled \ac{CDF}s converge weakly to a Brownian bridge,
\begin{equation*}
    \left\{\sqrt{p}\left(\widehat{F}_p(t) - t\right)\right\}_{t\in[0,1]} 
    % \stackrel{J_1}{\longrightarrow} 
    \implies
    \left\{\mathbb{B}(t)\right\}_{t\in[0,1]},\ \ \ \mbox{ as } p\to\infty,
\end{equation*}
under the global null $\mathcal{H}_0$ and mild continuity assumptions on the $F_i$'s \citep{skorokhod1956limit}. 
Therefore, goodness-of-fit statistics such as Kolmogorov-Smirnov distance \citep{smirnov1948table}, Cramer-von Mises-type statistics \citep{cramer1928composition, anderson1952asymptotic} that measure the departure from this limiting behavior can be used for testing $\mathcal{H}_0$ against $\mathcal{H}_1$.
Of particular interest is the higher criticism (\ac{HC}) statistic, first proposed by \cite{tukey1976lecture},
\begin{equation} \label{eq:HC-statistic}
    HC(x) = 
    \max_{0\le t\le\alpha_0}\frac{\widehat{F}_p(t) - t}{\sqrt{t(1 - t)/p}}.
\end{equation}

@@

Under the assumption that the data $x(i)$'s under the null have a common marginal distribution $F$, we review five thresholding procedures for support recovery, starting with the well-known Bonferroni's procedure which aims at controlling family-wise error rates.
\begin{definition}[Bonferroni's procedure]
Bonferroni's procedure with level $\alpha$ is the thresholding procedure that uses the threshold
\begin{equation} \label{eq:Bonferroni-procedure}
    t_p = F^{\leftarrow}(1 - \alpha/p).
\end{equation}
where  $F^{\leftarrow}(u)=\inf{\left\{x:F(x)\ge u\right\}}$ is the generalized inverse function.
\end{definition}
% It is easy to see that the family-wise error rate (FWER) is controlled at level $\alpha$ by applying the union bound, regardless of the error-dependence structure (see e.g.\ Relation \eqref{eq:Bonferroni-FWER-control}, below).
The Bonferroni procedure is deterministic, i.e. non data-dependent, and only depends on the dimension of the problem and the null distribution.
A closely related procedure is Sid\'ak's procedure \citep{vsidak1967rectangular},
which is a more aggressive (and also deterministic) thresholding procedure that uses the threshold
\begin{equation} \label{eq:Sidak-procedure}
    t_p = F^{\leftarrow}((1 - \alpha)^{1/p}).
\end{equation}
% can be shown to control FWER in the case independent errors.

@@

It can be shown that both Bonferroni's and Holm's procedures control FWER at their nominal levels, regardless of dependence in the 
data \citep{holm1979simple}. In contrast, Sid\'ak's and Hochberg's procedures control FWER at nominal levels when data are independent \citep{vsidak1967rectangular, hochberg1988sharper}. \stilian{DISCUSS}{Explain in the Supplement?}

@@

Recall the order statistics of our observations $x_{[1]} \ge x_{[2]}  \ge \ldots \ge x_{[p]}$.
\begin{definition}[Benjamini-Hochberg's procedure] \label{def:BH}
Let $i^*$ be the largest index such that
$$
\overline{F}(x_{[i]}) \le \alpha i/p.
$$
The Benjamini-Hochberg (BH) procedure with level $\alpha$ is the thresholding procedure with threshold
\begin{equation} \label{eq:BH-procedure}
    t_p(x) = x_{[i^*]},
\end{equation}
\end{definition}
The \ac{BH} procedure is shown to control the FDR at level $\alpha$ when the $x(i)$'s are independent \citep{benjamini1995controlling}. 
\stilian{DISCUSS}{Again, explain in the Supplement?} Variations of this procedure have been proposed to control the \ac{FDR} under certain models of dependent observations \citep{benjamini2001control}.

>>>>

While \eqref{eq:Lq-norm} measures the deviation of the data from the origin in an omnidirectional manner, statistics that are tailored to the alternatives can be used in the hopes of power improvement if the directions of the alternatives are known.
For example, in the additive error model \eqref{eq:model-additive}, suppose we want to test for positive mean shifts, i.e., one-sided alternative
\begin{equation} \label{eq:global-test-one-sided}
    %\mathcal{H}_0: \mu(i) = 0, \;i=1,\ldots,p,
    %\quad\text{v.s.}\quad 
    \mathcal{H}_1: \mu(i)> 0, \; \text{for some }i\in\{1,\ldots,p\}.
\end{equation}
Then, one might consider monitoring the sum (or equivalently, the arithmetic average) of the observations, 
\begin{equation} \label{eq:sum-statistic}
    T(x) := \sum_{i=1}^p{x(i)},
\end{equation}
or the maximum of the observations,
\begin{equation} \label{eq:max-statistic}
    M(x) := \max_{i=1,\ldots,p}{x(i)}.
\end{equation}
Other tests based on the empirical \ac{CDF} are also available.
Assuming the same one-sided alternative, let 
\begin{equation}
    q(i) = 1 - \sup\{F_i(y)\,:\,y<x(i)\}, \quad i = 1,\ldots,p,
\end{equation}
be the p-values of the individual observations, where $F_i$ is the \ac{CDF} of the $i$-th component $x(i)$ under $\mathcal{H}_0$.
We define empirical \ac{CDF} of the p-values as
\begin{equation}
    \widehat{F}_p(t) = 
    \frac{1}{p} \sum_{i=1}^p \mathbbm{1}_{[0, t]}(q(i)).
\end{equation}
Viewed as random elements in the space of c\`adl\`ag functions with the Skorohod $J_1$ topology, the centered and scaled \ac{CDF}s converge weakly to a Brownian bridge,
\begin{equation*}
    \left\{\sqrt{p}\left(\widehat{F}_p(t) - t\right)\right\}_{t\in[0,1]} 
    % \stackrel{J_1}{\longrightarrow} 
    \implies
    \left\{\mathbb{B}(t)\right\}_{t\in[0,1]},\ \ \ \mbox{ as } p\to\infty,
\end{equation*}
under the global null $\mathcal{H}_0$ and mild continuity assumptions on the $F_i$'s \citep{skorokhod1956limit}. 
Therefore, goodness-of-fit statistics such as Kolmogorov-Smirnov distance \citep{smirnov1948table}, Cramer-von Mises-type statistics \citep{cramer1928composition, anderson1952asymptotic} that measure the departure from this limiting behavior can be used for testing $\mathcal{H}_0$ against $\mathcal{H}_1$.
Of particular interest is the higher criticism (\ac{HC}) statistic, first proposed by \cite{tukey1976lecture},
\begin{equation} \label{eq:HC-statistic}
    HC(x) = 
    \max_{0\le t\le\alpha_0}\frac{\widehat{F}_p(t) - t}{\sqrt{t(1 - t)/p}}.
\end{equation}

@@

Under the assumption that the data $x(i)$'s under the null have a common marginal distribution $F$, we review five thresholding procedures for support recovery, starting with the well-known Bonferroni's procedure which aims at controlling family-wise error rates.
\begin{definition}[Bonferroni's procedure] \label{def:Bonf}
Bonferroni's procedure with level $\alpha$ is the thresholding procedure that uses the threshold
\begin{equation} \label{eq:Bonferroni-procedure}
    t_p = F^{\leftarrow}(1 - \alpha/p).
\end{equation}
where  $F^{\leftarrow}(u)=\inf{\left\{x:F(x)\ge u\right\}}$ is the generalized inverse function.
\end{definition}
% It is easy to see that the family-wise error rate (FWER) is controlled at level $\alpha$ by applying the union bound, regardless of the error-dependence structure (see e.g.\ Relation \eqref{eq:Bonferroni-FWER-control}, below).
The Bonferroni procedure is deterministic, i.e. non data-dependent, and only depends on the dimension of the problem and the null distribution.
A closely related procedure is Sid\'ak's procedure \citep{vsidak1967rectangular},
which is a more aggressive (and also deterministic) thresholding procedure that uses the threshold
\begin{equation} \label{eq:Sidak-procedure}
    t_p = F^{\leftarrow}((1 - \alpha)^{1/p}).
\end{equation}
% can be shown to control FWER in the case independent errors.

@@

It can be shown that both Bonferroni's and Holm's procedures control FWER at their nominal levels, regardless of dependence in the 
data \citep{holm1979simple}. In contrast, Sid\'ak's and Hochberg's procedures control FWER at nominal levels when data are independent \citep{vsidak1967rectangular, hochberg1988sharper}.

@@

Recall the order statistics of our observations are: $x_{[1]} \ge x_{[2]}  \ge \ldots \ge x_{[p]}$.
\begin{definition}[Benjamini-Hochberg's procedure] \label{def:BH}
Let $i^*$ be the largest index such that
$$
\overline{F}(x_{[i]}) \le \alpha i/p.
$$
The Benjamini-Hochberg (BH) procedure with level $\alpha$ is the thresholding procedure with threshold
\begin{equation} \label{eq:BH-procedure}
    t_p(x) = x_{[i^*]},
\end{equation}
\end{definition}
The \ac{BH} procedure is shown to control the FDR at level $\alpha$ when the $x(i)$'s are independent \citep{benjamini1995controlling}. 
 Variations of this procedure have been proposed to control the \ac{FDR} under certain models of dependent observations \citep{benjamini2001control}.

### 2021-02-03 3.phase_transitions/3.Gaussian-support-recovery.tex
DONE!
Ready for one final pass. Specifically, in the PDF, pls look at pages:

29, 30, 60 (notation <...>) Proofs of Propositons 5.1 and 5.3, Def. 5.3.

Page 115.

There is only one UNDEFINED reference on page 115. I can fix it once I understand the context better.

\stilian{
Figure \ref{fig:phase-Gaussian-errors} illustrates the rich landscape of phase transitions in support recovery for the various choices
of statistical risk for the family of thresholding estimators, established in the following sections.}{\fbox{ added these words and moved the figure here}}
We end this brief overview with a technical notion needed in order to state our main results.
We define a rate at which the nominal levels of FWER or FDR go to zero.
\begin{definition} \label{def:slowly-vanishing}
We say the nominal level of errors $\alpha = \alpha_p$ vanishes slowly, if
\begin{equation} \label{eq:slowly-vanishing-error}
    \alpha\to 0,\quad \text{and} \quad \alpha p^\delta\to\infty \text{  for any } \delta>0.
\end{equation}
\end{definition}
As an example, the sequence of nominal levels $\alpha_p = 1/\log{(p)}$ is slowly vanishing, while the sequence $\alpha_p = 1/\sqrt{p}$ is not.

@@

\stilian{We end this chapter with a general discussion on the effect of the signal sparsity on the interplay between 
signal size and sparsity in the context of the detection and
 support recovery problems.  Specifically, different support recovery criteria are compared.}{\fbox{added, check}}

>>>>

Figure \ref{fig:phase-Gaussian-errors} illustrates the rich landscape of phase transitions in support recovery for the various choices
of statistical risk for the family of thresholding estimators, established in the following sections.
We end this brief overview with a technical notion needed in order to state our main results.
We define a rate at which the nominal levels of FWER or FDR go to zero.
\begin{definition} \label{def:slowly-vanishing}
We say the nominal level of errors $\alpha = \alpha_p$ vanishes slowly, if
\begin{equation} \label{eq:slowly-vanishing-error}
    \alpha\to 0,\quad \text{and} \quad \alpha p^\delta\to\infty \text{  for any } \delta>0.
\end{equation}
\end{definition}
As an example, the sequence of nominal levels $\alpha_p = 1/\log{(p)}$ is slowly vanishing, while the sequence $\alpha_p = 1/\sqrt{p}$ is not.

@@

%We end this chapter with a general discussion on the effect of the signal sparsity on the interplay between 
%signal size and sparsity in the context of the detection and
% support recovery problems.  Specifically, different support recovery criteria are compared.

### 2021-02-03 3.phase_transitions/3.global-tests.tex
DONE!
Ready for one final pass. Specifically, in the PDF, pls look at pages:

29, 30, 60 (notation <...>) Proofs of Propositons 5.1 and 5.3, Def. 5.3.

Page 115.

There is only one UNDEFINED reference on page 115. I can fix it once I understand the context better.

\stilian{For simplicity of the exposition, we will suppose that  in \eqref{eq:signal-size-small} we have 
$\underline{r} = r = \overline{r}$, so that  $\mu(i) = p^r$.  The general case where $\underline{r}<\overline{r}$ is left as 
an exercise.}{\fbox{How about that?}}

>>>>

For simplicity of the exposition, we will suppose that  in \eqref{eq:signal-size-small} we have 
$\underline{r} = r = \overline{r}$, so that  $\mu(i) = p^r$.  The general case where $\underline{r}<\overline{r}$ is left as 
an exercise.

### 2021-02-03 5.Bayes.optimality/5.Bayes_optimality_and_minimax.tex
working on ch. 6
implementing my corrections.
DONE!
Ready for one final pass. Specifically, in the PDF, pls look at pages:

29, 30, 60 (notation <...>) Proofs of Propositons 5.1 and 5.3, Def. 5.3.

Page 115.

There is only one UNDEFINED reference on page 115. I can fix it once I understand the context better.

\stilian{ 
For any collection of numbers $\{a_i,\ i=1,\cdots,s\}$, let 
$$
\langle a_1,\cdots,a_s\rangle := (a_{[1]},\cdots,a_{[s]})
$$
denote the vector of $a_i$'s arranged in a non-increasing order.

@@

 Simply put, the oracle thresholding estimators are comprised of the indices corresponding to the $s$ largest values in the
 data.  Note that, in the absence of ties among the largest $s+1$ data values, the oracle thresholding estimator is unique.  
 For concreteness,  one can break possible ties lexicographically.  In many cases, 
 the oracle thresholding estimators will be almost surely unique.}
{\fbox{IMPORTANT, replacing the following}
\begin{definition}[Oracle data thresholding]
We call $\widehat{S}^* = \{i\,|\, x(i)\ge x_{[s]}\}$ the oracle data thresholding procedure, where $x_{[1]} \ge \ldots \ge x_{[p]}$ are the order statistics of $x$.
\end{definition}}

@@

Since $x(j) < x(j')$, and since each of $\{f_0, f_{i}\}$ is an MLR family, we have
$$
\frac{f_i(x(j))}{f_0(x(j))} - \frac{f_i(x(j'))}{f_0(x(j'))} \le 0 \implies f_i(x(j)) f_0(x(j')) - f_i(x(j')) f_0(x(j)) \le 0.
$$
Using Relation \eqref{eq:MLR-optimality-proof}, we conclude that $f(x|\widehat{S}) \le f(x|\widehat{S}\,')$.
\stilian{Continuing this way, we can successively improve the likelihood of every estimator until we arrive at an oracle thresholding estimator, proving the desired optimality.  Note that with the same argument, we obtain that any two oracle 
thresholding estimators have the same likelihood.}{
\fbox{replacing} This implies that any estimator that is not $\widehat{S}^*$ may be improved, and the optimality follows.}
\end{proof}

@@

When the MLR condition in Proposition \ref{prop:optimal-oracle-procedures} is violated, the oracle thresholding 
procedures can in fact be sub-optimal (see Example \ref{exmp:suboptimal-data-thresholding} and 
Section \ref{sec:sup-optimality-of-thresholding}, below).  
%
\stilian{In this section, we demonstrate that thresholding the \emph{likelihood ratio} rather than signal values
yields the finite-sample Bayes optimal procedures.  We consider a special but sufficiently general case of signal 
models with equal densities.

@@

\begin{definition}[Oracle likelihood ratio thresholding] Recall that $\langle a_1,\cdots,a_s\rangle$ denotes
the vector of $a_i$'s arranged in a non-increasing order.  Any estimator $\hat S = \{i_1,\cdots,i_s\}$ such that
$$
\langle L(i_1),\cdots,L(i_s) \rangle = (L_{[1]},\cdots,L_{[s]}),
$$
will be referred to as an {\em oracle likelihood thresholding} estimator of the support $S$.
\end{definition}
\begin{proposition} \label{prop:likelihood-ratio-thresholding} Any oracle likelihood ratio thresholding 
procedure $\widehat{S}_{\text{LRT}}$ is finite-sample optimal in terms of Bayes risk. That is,
\begin{equation}
    \widehat{S}_{\text{LRT}} \in \argmin_{\widehat{S} \in {\mathcal S}} \E_\pi \P[\widehat{S} \neq S].
\end{equation}
for all $s$ and $p$, where the infimum on $\widehat{S}$ is taken over all support estimators of size $s$.
\end{proposition} 
}{Introducing part of the proposition as a definition....}

\stilian{NOTE}{This change \& definition
 was motivated by the annoying fact that we could have ties among the likelihood ratios.  Also, to my understanding we
 must LIMIT OURSELVES to estimators of size $s$, so we should limit $|\widehat{S}_{{\rm LRT}}|$ to $s$. \fbox{CORRECT?} I am SORRY if I made a MESS.}

\begin{proof}%[Proof of Proposition \ref{prop:likelihood-ratio-thresholding}]
The proof is analogous to that of Proposition \ref{prop:optimal-oracle-procedures}.
We need to show that
$
\widehat{S}_{\rm LRT} \in \argmax_{S \in \mathcal{S}} f(x|S) \pi(S).
$
Since the distribution $\pi$ of the support $S$ 
is uniform (recall \eqref{eq:uniform}), it is equivalent to prove that 
$$
f(x|\widehat{S}_{\text{LRT}}) = \max_{S \in \mathcal {S}} f(x|S),
$$ 
where  $f(x|S)$ is the conditional distribution of the data given the unordered support $S$,
\begin{equation} \label{eq:likelihood-ratio-thresholding-proof}
    f(x|S) = \sum_P f(x|P) \pi^{\text{ord}}(P|S) = \prod_{j\in S} f_a(x(j)) \prod_{j\not\in S}{f_0(x(j))}.
\end{equation}
Suppose $\widehat S\in {\mathcal S}$ is {\em not} an oracle likelihood thresholding estimator. 
Then from the definition of the likelihood ratio thresholding procedure, there 
must be indices 
$j \in \widehat S$ and $j' \not \in \widehat{S}$ such that $L(j) < L(j')$.
If we exchange the labels of $L(j)$ and $L(j')$, that is, we form a new estimate 
$\widehat{S}\,' = \big(\widehat{S}\setminus\{j\}\big)\cup\{j'\}$,
comparing the log-likelihoods under $\widehat{S}$ and $\widehat{S}\,'$, we have
\begin{equation*}
    \log{f(x|\widehat{S})} - \log{f(x|\widehat{S}\,')} 
    = \log{f_a(x(j))} + \log{f_0(x(j'))} - \log{f_a(x(j'))} - \log{f_0(x(j))}.
\end{equation*}
By the definition of $L(j)$'s, and the order relations, we obtain
\begin{equation*}
    \log{f(x|\widehat{S})} - \log{f(x|\widehat{S}\,')} 
    = \log{L(j)} - \log{L(j')} > 0
\end{equation*}
\stilian{This shows that $\widehat S$ cannot be Bayes optimal unless it is a likelihood thresholding estimator.
Note that with the same argument for every two likelihood thresholding estimators $\widehat S'$
and $\widehat S''$, we have $ f(x|\widehat{S}') = f(x|\widehat{S}'')$, proving the desired optimality.
}{\fbox{Please check.} See also the change in the oracle thresholding argument.}
\end{proof}

@@

\stilian{NEEDS}{WORK}

>>>>

%\stilian{ 
For any collection of numbers $\{a_i,\ i=1,\cdots,s\}$, let 
$$
\langle a_1,\cdots,a_s\rangle := (a_{[1]},\cdots,a_{[s]})
$$
denote the vector of $a_i$'s arranged in a non-increasing order.

@@

 Simply put, the oracle thresholding estimators are comprised of the indices corresponding to the $s$ largest values in the
 data.  Note that, in the absence of ties among the largest $s+1$ data values, the oracle thresholding estimator is unique.  
 For concreteness,  one can break possible ties lexicographically.  In many cases, 
 the oracle thresholding estimators will be almost surely unique.
 %}
%{\fbox{IMPORTANT, replacing the following}
%\begin{definition}[Oracle data thresholding]
%We call $\widehat{S}^* = \{i\,|\, x(i)\ge x_{[s]}\}$ the oracle data thresholding procedure, where $x_{[1]} \ge \ldots \ge x_{[p]}$ are the order statistics of $x$.
%\end{definition}}

@@

Since $x(j) < x(j')$, and since each of $\{f_0, f_{i}\}$ is an MLR family, we have
$$
\frac{f_i(x(j))}{f_0(x(j))} - \frac{f_i(x(j'))}{f_0(x(j'))} \le 0 \implies f_i(x(j)) f_0(x(j')) - f_i(x(j')) f_0(x(j)) \le 0.
$$
Using Relation \eqref{eq:MLR-optimality-proof}, we conclude that $f(x|\widehat{S}) \le f(x|\widehat{S}\,')$.
Continuing this way, we can successively improve the likelihood of every estimator until we arrive at an oracle thresholding estimator, proving the desired optimality.  Note that with the same argument, we obtain that any two oracle 
thresholding estimators have the same likelihood.
\end{proof}

@@

When the MLR condition in Proposition \ref{prop:optimal-oracle-procedures} is violated, the oracle thresholding 
procedures can in fact be sub-optimal (see Example \ref{exmp:suboptimal-data-thresholding} and 
Section \ref{sec:sup-optimality-of-thresholding}, below).  
%

In this section, we demonstrate that thresholding the \emph{likelihood ratio} rather than signal values
yields the finite-sample Bayes optimal procedures.  We consider a special but sufficiently general case of signal 
models with equal densities.

@@

\begin{definition}[Oracle likelihood ratio thresholding] Recall that $\langle a_1,\cdots,a_s\rangle$ denotes
the vector of $a_i$'s arranged in a non-increasing order.  Any estimator $\hat S = \{i_1,\cdots,i_s\}$ such that
$$
\langle L(i_1),\cdots,L(i_s) \rangle = (L_{[1]},\cdots,L_{[s]}),
$$
will be referred to as an {\em oracle likelihood thresholding} estimator of the support $S$.
\end{definition}
\begin{proposition} \label{prop:likelihood-ratio-thresholding} Any oracle likelihood ratio thresholding 
procedure $\widehat{S}_{\text{LRT}}$ is finite-sample optimal in terms of Bayes risk. That is,
\begin{equation}
    \widehat{S}_{\text{LRT}} \in \argmin_{\widehat{S} \in {\mathcal S}} \E_\pi \P[\widehat{S} \neq S].
\end{equation}
for all $s$ and $p$, where the infimum on $\widehat{S}$ is taken over all support estimators of size $s$.
\end{proposition}

\begin{proof}%[Proof of Proposition \ref{prop:likelihood-ratio-thresholding}]
The proof is analogous to that of Proposition \ref{prop:optimal-oracle-procedures}.
We need to show that
$
\widehat{S}_{\rm LRT} \in \argmax_{S \in \mathcal{S}} f(x|S) \pi(S).
$
Since the distribution $\pi$ of the support $S$ 
is uniform (recall \eqref{eq:uniform}), it is equivalent to prove that 
$$
f(x|\widehat{S}_{\text{LRT}}) = \max_{S \in \mathcal {S}} f(x|S),
$$ 
where  $f(x|S)$ is the conditional distribution of the data given the unordered support $S$,
\begin{equation} \label{eq:likelihood-ratio-thresholding-proof}
    f(x|S) = \sum_P f(x|P) \pi^{\text{ord}}(P|S) = \prod_{j\in S} f_a(x(j)) \prod_{j\not\in S}{f_0(x(j))}.
\end{equation}
Suppose $\widehat S\in {\mathcal S}$ is {\em not} an oracle likelihood thresholding estimator. 
Then from the definition of the likelihood ratio thresholding procedure, there 
must be indices 
$j \in \widehat S$ and $j' \not \in \widehat{S}$ such that $L(j) < L(j')$.
If we exchange the labels of $L(j)$ and $L(j')$, that is, we form a new estimate 
$\widehat{S}\,' = \big(\widehat{S}\setminus\{j\}\big)\cup\{j'\}$,
comparing the log-likelihoods under $\widehat{S}$ and $\widehat{S}\,'$, we have
\begin{equation*}
    \log{f(x|\widehat{S})} - \log{f(x|\widehat{S}\,')} 
    = \log{f_a(x(j))} + \log{f_0(x(j'))} - \log{f_a(x(j'))} - \log{f_0(x(j))}.
\end{equation*}
By the definition of $L(j)$'s, and the order relations, we obtain
\begin{equation*}
    \log{f(x|\widehat{S})} - \log{f(x|\widehat{S}\,')} 
    = \log{L(j)} - \log{L(j')} > 0
\end{equation*}
This shows that $\widehat S$ cannot be Bayes optimal unless it is a likelihood thresholding estimator.
Note that with the same argument for every two likelihood thresholding estimators $\widehat S'$
and $\widehat S''$, we have $ f(x|\widehat{S}') = f(x|\widehat{S}'')$, proving the desired optimality.
\end{proof}

@@
